Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-06-15 FIE2019-final-TPJHD.tex
JHD's version

Evaluating how cybersecurity is taught in all aspects of computer science is a  task of considerable size. We feel that to do this completely is beyond the scope of our current research and the scope of this paper. We have instead adopted a case study based research approach to evaluate the evidence of the teaching of cybersecurity within general computer science to undergraduate students. Thus, in the context of widespread international computer science/engineering curriculum reform - both in compulsory, as well as post-compulsory education - what does this need to embed cybersecurity mean more generally for institutions and educators, and how do we teach this curricula area?

>>>>

Evaluating how cybersecurity is taught in all aspects of computer science is a  task of considerable size. We feel that to do this completely is beyond the scope of our current research and the scope of this paper. We have instead adopted a case study based research approach to evaluate the evidence of the teaching of cybersecurity within general computer science to undergraduate students. Thus, in the context of widespread international computer science/engineering curriculum reform, %- both in compulsory, as well as post-compulsory education - 
what does this need to embed cybersecurity mean more generally for institutions and educators, and how do we teach this subject?
